SiO Molecular Jets around young stars - A numerical perspective

### 2013-07-29 PAPER/ms_final_bv.tex
Added new figs

\begin{figure}
 \includegraphics[width=84mm]{\figpath/abun.png}
 \caption{The polynomial used to calculate an abundance of SiO as a function of local velocity.}
 \label{abun}
\end{figure}

@@

Effects of varing abundance profile ... Crucial ingredient in
modeling molecular bullets \\

@@

Comparison with Observed results \\
Different line transition trace different components of SiO
emission. The low level transitions trace the region where the jet
interacts with molecular medium. The clumpy nature in its emission is
from the turbulent nature of its interaction. The higher transitions
trace a much more collimated region along with the terminal shock. 
As seen by Chandler \& Richer 2001 and Hirano 2006.
\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/linejets.png}
 \caption{SiO emission from different line transitions for the run with molecular
   cooling having $\eta$ = 3 and $\beta$ = 10. }
\label{grid}
\end{figure*}

Advantage of non-LTE modeling over LVG Cabrit 2007, Lee 2008. 
Line ratios $\sim$ 1 can be explained well. \\

>>>>

\begin{figure}
 \includegraphics[width=84mm]{\figpath/diffabun.png}
 \caption{The different fractional SiO abundances as a function of
   shock velocity, V${\rm s}$.}
 \label{abun}
\end{figure}

@@

Effects of varing abundance profile ... Crucial ingredient in
modeling molecular bullets \\
\begin{figure}
 \includegraphics[width=1.\columnwidth]{\figpath/EM_diffabun.png}
 \caption{Variation of 2-$>$1 SiO emission for runs with molecular
   cooling having $\eta$ = 3 and $\beta$ = 10 and different abundance profiles.}
\label{grid}
\end{figure}

\begin{figure}
 \includegraphics[width=1.\columnwidth]{\figpath/PV_diffabun.png}
 \caption{Variation of position-velocity diagram for 2-$>$1 SiO emission for runs with molecular
   cooling having $\eta$ = 3 and $\beta$ = 10 and different abundance profiles.}
\label{grid}
\end{figure}

@@

Comparison with Observed results \\
Different line transition trace different components of SiO
emission. The low level transitions trace the region where the jet
interacts with molecular medium. The clumpy nature in its emission is
from the turbulent nature of its interaction. The higher transitions
trace a much more collimated region along with the terminal shock. 
As seen by Chandler \& Richer 2001 and Hirano 2006.
\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/linejets_thnolog.png}
 \caption{SiO emission from different line transitions for the run with molecular
   cooling having $\eta$ = 3 and $\beta$ = 10 using top-hat fractional
   abundance profile. }
\label{grid}
\end{figure*}

Advantage of non-LTE modeling over LVG Cabrit 2007, Lee 2008. 
Line ratios $\sim$ 1 can be explained well. \\
\begin{figure}
 \includegraphics[width=1.\columnwidth]{\figpath/LineRatio_TH_60_Y205.png}
 \caption{{\em{Top}} Line profiles in SiO J = 2-1, 5-4 and 8-7 at one
   the inner knot for the molecular cooling run with $\eta$ = 3 and
   $\beta$ = 10 using top hat abundance profile. The profiles are
   obatined when the angle of inclination is 60$^{\circ}$ with respect
 to line of sight. {\em{Bottom}} Line temperature ratios T(8-7)/T(5-4)
and T(2-1)/T(5-4), as a function of velocity}
\label{grid}
\end{figure}
